\documentclass[sigconf]{acmart}

\usepackage{booktabs} % For formal tables

\usepackage{graphicx}
\usepackage{balance}  % for  \balance command ON LAST PAGE  (only there!)

\usepackage[linesnumbered]{algorithm2e}
\usepackage{caption}
\usepackage{subcaption}
\captionsetup[subfigure]{labelformat = parens, labelsep = space, font = small}
\usepackage{enumitem}


%\usepackage{algorithm}
%\usepackage{algpseudocode}

% To get colored comments
\usepackage{color}  
\newcommand{\johannes}[1]{{\color{blue} Johannes: [{#1}]}}
\newcommand{\lucja}[1]{{\color{red} Lucja: [{#1}]}}
\newcommand{\bailu}[1]{{\color{cyan} Bailu: [{#1}]}}
\newcommand{\magda}[1]{{\color{magenta} Magda: [{#1}]}}

\newcommand{\eat}[1]{} % comment out blocks of text

% Copyright
%\setcopyright{none}
%\setcopyright{acmcopyright}
%\setcopyright{acmlicensed}
\setcopyright{rightsretained}
%\setcopyright{usgov}
%\setcopyright{usgovmixed}
%\setcopyright{cagov}
%\setcopyright{cagovmixed}


% DOI
%\acmDOI{10.475/123_4}

% ISBN
%\acmISBN{123-4567-24-567/08/06}

%Conference
\acmConference[SIGMOD'18]{ACM SIGMOD International Conference on Management of Data}{June 2018}{Houston, Texas, USA} 
\acmYear{2018}
\copyrightyear{2018}

%\acmPrice{15.00}

\begin{document}

% ****************** TITLE ****************************************

\title{Improving OCC Performance Through Transaction Batching and Operation Reordering}

%\author{
% You can go ahead and credit any number of authors here,
% e.g. one 'row of three' or two rows (consisting of one row of three
% and a second row of one, two or three).
%
% The command \alignauthor (no curly braces needed) should
% precede each author name, affiliation/snail-mail address and
% e-mail address. Additionally, tag each line of
% affiliation/address with \affaddr, and tag the
% e-mail address with \email.
%
% 1st. author
%\alignauthor Bailu Ding \\
%	\affaddr{Cornell University, Microsoft Research}\\
%    \email{badin@microsoft.com}
% 2nd. author
%\alignauthor Lucja Kot \\
%	\affaddr{Cornell University}\\
%    \email{lucja@cs.cornell.edu}
% 3rd. author
%\alignauthor Magdalena Balazinska\\
%	\affaddr{University of Washington}\\
%	\affaddr{Seattle, Washington, USA}\\
%    \email{magda@cs.washington.edu}
%\and
%\alignauthor Johannes Gehrke\\
%	\affaddr{Microsoft Corporation}\\
%    \email{johannes@microsoft.com}
%}

\begin{abstract}
	OLTP systems can often improve throughput by \emph{batching} transactions and processing them as a group. Batching has been used for optimizations such as message packing and group commits; however, there is little research on the benefits of a holistic approach to batching across a transaction's entire life cycle.
	
In this paper, we present an OLTP system based on optimistic concurrency control that incorporates batching at multiple stages of transaction execution. 
%Execution batching enables enables reordering of operations to improve performance and reduce conflicts: 
Storage batching enables reordering of transaction reads and writes at the storage layer, reducing same object conflicts. Validator batching enables reordering of transactions before validation, reducing inter-batch conflicts. Dependencies between transactions make transaction reordering a non-trivial problem, and we propose several several efficient and practical algorithms that can be customized to various transaction precedence policies such as reducing tail latency. We also show how to parallelize validator batching for better performance. 

An in-depth evaluation on both prototype and production system shows that our techniques can significantly increase system throughput and reduce latency, including tail latencies. 
\end{abstract}

\maketitle

\input{introduction}
\input{background}
%\input{overview}
%\input{reorder}
\input{method}
\input{experiment}
\input{related}
\input{conclusion}

\bibliographystyle{abbrv}
\bibliography{reference}

\end{document}
